Collective excitations in competing phases in two and three dimensions

### 2024-03-05 paper/main.tex
Paper stuff

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_details.pdf}
    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{l.AFM}$ relative to the lower edge of the two-particle continuum $\omega_-$.
    The lower panels (b) depict their respective weights $W_0$.
    Again, we chose $V=1.2t$ for the square lattice (left column) and $V=0.8t$ for the simple cubic lattice (right column) respectively.
    $U_0$ denotes the highest value of $U$ for which there is no peak below the two-particle continuum.
    For the square lattice, it is $U_0 \approx 3.372t$ and for the simple cubic lattice, it is $U_0 \approx 4.479t$.
    The parameter range depicted here places the system within the CDW phase.
    The fits are of the same fashion as in \autoref{fig:sc_in_cdw_behavior}.}
    \label{fig:afm_cdw_peaks_details}
\end{figure*}

@@

Additionally, we plot in (b) the peak positions relative to the lower edge of the two-particle continuum.
We see that the lower-lying peak, i.e., the peak corresponding to the phase the system is in, 
strays further away from the continuum as the system moves away from the phase boundary.
The other peak, however, moves ever closer to the aforementioned continuum until they reach it.
At this point, the weight of said peak also vanishes, see panel (c).
This occurs around $U \approx 4.8t \pm 1.428t$ for the square lattice and around $U \approx 4.8t \pm 0.321t$ for the simple cubic lattice.

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/afm_cdw_peaks_details.pdf}
    \caption{The upper panels (a) show double logarithmic plots of the positions $\omega_0$ of the peak in $\spectral{l.AFM}$ relative to the lower edge of the two-particle continuum $\omega_-$.
    The lower panels (b) depict their respective weights $W_0$.
    Again, we chose $V=1.2t$ for the square lattice (left column) and $V=0.8t$ for the simple cubic lattice (right column) respectively.
    $U_0$ denotes the highest value of $U$ for which there is no peak below the two-particle continuum.
    For the square lattice, it is $U_0 = 3.38$ and for the simple cubic lattice, it is $U_0 = 4.48t$.
    The parameter range depicted here places the system within the CDW phase.
    The fits are of the same fashion as in \autoref{fig:sc_in_cdw_behavior}.}
    \label{fig:afm_cdw_peaks_details}
\end{figure*}

@@

Additionally, we plot in (b) the peak positions relative to the lower edge of the two-particle continuum.
We see that the lower-lying peak, i.e., the peak corresponding to the phase the system is in, 
strays further away from the continuum as the system moves away from the phase boundary.
The other peak, however, moves ever closer to the aforementioned continuum until they reach it.
At this point, the weight of said peak also vanishes, see panel (c).
This occurs around $U \approx 4V \pm 0.4245t$ for the square lattice and around $U \approx 6V \pm 1.11t$ for the simple cubic lattice.
